### 2015-06-22 text/ms.Rmd
More discussion editing

Certain conditions will make some ensemble models more effective than others. First, ensemble models will be most effective when they are comprised of diverse individual models that make substantially different assumptions about underlying dynamics, or make different but plausible assumptions about certain parameter values [e.g. @ali1996; @tebaldi2007]. Such models would be expected to perform well across different conditions and an ensemble model can exploit the best predictive performance of each model. Second, ensemble models will be most effective when they are not overfit to training data. The probability of overfitting ensemble models generally increases with the number of individual models [e.g. @caruana2004]. Cross-validation testing, information theoretic methods (e.g. AIC), and methods that are robust to over-fitting such as random forests (REF), may help avoid overfitting ensemble models. We note that our simplest ensemble model, a mean of the individual model predictions, performed approximately as well as the complex machine learning models when we applied our ensembles to an entirely new dataset (FIG). Third, ensemble models will be most effective when they are trained on data that are representative of the dataset of interest. Cross-validation within a training dataset will provide a optimistically biased impression of predictive performance if the training dataset fundamentally differs from the dataset of interest.

Ensemble models share similarities with coefficient averaging (Burnham and Anderson REF) but differ in many important way. At a high level, ensemble models and coefficient averaging share the same idea that no one model is correct and multiple models can contribute useful information for inference. A fundamental difference between coefficient averaging and ensemble models is that coefficient averaging focuses on a averaging *coefficients* whereas ensembles instead average *predictions*. By focussing on predictions, ensembles are a more general purpose tool: they don't require information theoretics, they can combine completely different types of models (e.g. combining parametric and non-parametric models or frequentist and Bayesian predictions), and they can combine predictions in complex non-linear ways that also depend on additional covariates.

A strength of ensemble models is that they can be tailored or specific response variables. For example, we built separate models of mean \bbmsy\\ and the slope of \bbmsy\\. The same set of model weights or non-linear relationships need not hold across different response variables. Ensemble models can optimally combine the individual models depending on the response. Ensemble models could be combined to estimate any number of response variables of interest. For example, they could be combined to estimate a binary response such as whether status is above or below some threshold.

>>>>

Certain conditions will make some ensemble models more effective than others. First, ensemble models will be most effective when they are comprised of diverse individual models that make different assumptions about underlying dynamics, or make contrasting but plausible assumptions about parameter values [e.g. @ali1996; @tebaldi2007]. Such individual models would be expected to perform well across a variety of conditions and an ensemble model can exploit the best predictive performance of each. Second, ensemble models will be most effective when they are not overfit to the training dataset. The probability of overfitting ensemble models generally increases with the number of individual models [e.g. @caruana2004]. Cross-validation testing, information theoretic methods (e.g. AIC), and methods that are robust to over-fitting such as random forests (REF), may help avoid overfitting ensemble models. We note that our simplest ensemble model, a mean of the individual model predictions, performed approximately as well as the complex machine learning models when we applied our ensembles to an entirely new dataset (FIG). Third, ensemble models will be most effective when they are trained on data that are representative of the dataset of interest. Cross-validation within a training dataset will provide a optimistically biased impression of predictive performance if the training dataset fundamentally differs from the dataset of interest.

Ensemble models share similarities with coefficient averaging [@burnham2002] but differ other important ways. Ensemble models and coefficient averaging share the same notion that no one model is correct and multiple models can contribute useful information for inference. A fundamental difference between coefficient averaging and ensemble models is that coefficient averaging focuses on a averaging *coefficients* whereas ensembles instead average *predictions*. By focussing on predictions, ensembles are a more general purpose tool: they do not require information theoretics, they can combine different types of models (e.g. combining parametric and non-parametric models or frequentist and Bayesian predictions), and they can combine predictions in complex non-linear ways that may depend on additional covariates.

A strength of ensemble models is that they can be tailored or specific response variables. For example, we built separate models of mean \bbmsy\\ and the slope of \bbmsy\\. The same set of model weights or non-linear relationships need not hold across different response variables: ensemble models can optimally combine the individual models depending on the response. Ensemble models could be combined to estimate any number of response variables of interest. For example, they could be combined to estimate a binary response such as whether status is above or below some threshold.
